---
title: "How to Use Ezviewr"
author: "JooYoung Seo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use Ezviewr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ezviewr

The goal of ezviewr is to provide R users with convenient function to open their data objects with their preferable spreadsheet application window (e.g., Excel).

## Installation

### Development Version

You can install the latest development version as follows:

```{r, eval=F}
if(!require(devtools)) {
install.packages("devtools")
}

devtools::install_github('jooyoungseo/ezviewr')
```

### Stable Version

You can install the released version of ezviewr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ezviewr")
```

## Example

You can open any data.frame, tibble, matrix, or vector from an R session into your default-set spreadsheet application window as follows:


```{r example, eval=F}
library(ezviewr)

data(airquality)
str(airquality)

# Use `view()` function to open your data object in your spreadsheet:
view(airquality)
# Then, when necessary, you can modify the opened data in the spreadsheet and save it as a new data.
```
